---
title: "BCA Protein Assay"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_samples  <- <<<N_SAMPLES>>>
replicates <- 3      # wells per sample
n_standards <- 6     # Std 1–5 + blank
n_blanks    <- 3     # blank replicates
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Samples** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagent volumes for <<<N_SAMPLES>>> samples",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Protocol

### 1. Prepare Samples

1.1 Thaw homogenised muscle samples on ice. **Vortex thoroughly** before pipetting.

1.2 Re-freeze samples briefly, then thaw on ice again. **Vortex a second time**, then centrifuge at **10,000×g for 1 minute** to pellet any insoluble material.

*Note: the double freeze–thaw–vortex cycle helps resuspend sticky homogenates and improves pipetting accuracy.*

1.3 Prepare a **1:10 dilution** of each sample: aspirate **25 µL** of sample (post-centrifuge supernatant) into a new labelled tube. Add **225 µL** ice-cold MQH\textsubscript{2}O.

\textcolor{red}{Record any samples that appeared unusual, could not be vortexed, or were skipped.}

**Samples to process:**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

### 2. Prepare BCA Working Reagent

2.1 Calculate total volume required:

```{r working-reagent}
n_wells_total <- (n_samples * replicates) + (n_standards * replicates) + n_blanks
excess_factor <- 1.10

total_ul   <- n_wells_total * 200 * excess_factor
vol_A_ul   <- total_ul * (50 / 51)
vol_B_ul   <- total_ul * (1  / 51)

wr_tbl <- tibble(
  Component       = c("Reagent A (50 parts)", "Reagent B (1 part)", "Total (A + B)"),
  `Volume (µL)`   = sprintf("%.0f", c(vol_A_ul, vol_B_ul, total_ul)),
  `Volume (mL)`   = sprintf("%.1f", c(vol_A_ul, vol_B_ul, total_ul) / 1000)
)

kable(wr_tbl,
      caption = sprintf("BCA Working Reagent for %d samples × %d replicates + %d standards + %d blanks (10%% excess)",
                        n_samples, replicates, n_standards, n_blanks),
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

2.2 Mix Reagent A and Reagent B at **50:1 (A:B)**. Mix by gentle inversion.

\textcolor{red}{Working reagent volumes used — Reagent A: \_\_\_ µL, Reagent B: \_\_\_ µL}

### 3. Load Plate

3.1 Load **10 µL** of blank, standard, or 1:10 diluted sample into each well according to the plate map.

3.2 Add **200 µL** BCA working reagent to each well.

3.3 Cover plate. Incubate at **37°C for 30 minutes**.

3.4 Read absorbance at **562 nm**.

**Standards:**

| Standard | Concentration (mg/mL) |
|---|---|
| Blank | 0 |
| Std 1 | 0.125 |
| Std 2 | 0.25 |
| Std 3 | 0.5 |
| Std 4 | 1.0 |
| Std 5 | 2.0 |

\textcolor{red}{Attach or sketch plate map below.}

\vspace{5cm}

---

\newpage

## Results

Complete \texttt{results/results.csv} after analysis. Protein concentration in mg/mL derived from standard curve.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "BCA Assay Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "5cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, unusual samples, or lot number changes here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
