---
title: "Differentiation of Primary Human Skeletal Muscle Cells"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_wells <- <<<N_SAMPLES>>>
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date (seeding)** | <<<DATE>>> |
| **Wells** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagents and materials",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Media Formulas

### Growth Media (GM)
| Reagent | Volume | Catalogue |
|---|---|---|
| Ham's F-10 GlutaMAX | 500 mL | Gibco 41550-088 |
| FBS (South American origin) | 100 mL | Gibco 10270-106 |
| Pen/Strep | 5 mL | Gibco 15140-122 |
| Fungizone (Amphotericin B 250 µg/mL) | 5 mL | Gibco 15290-026 |

### Differentiation Media 1 (DM1)
| Reagent | Volume | Catalogue |
|---|---|---|
| DMEM GlutaMAX, 1 g/L glucose (low glucose) | 500 mL | Gibco 21885-108 |
| FBS | 50 mL | Gibco 10270-106 |
| Pen/Strep | 5 mL | Gibco 15140-122 |

### Differentiation Media 2 (DM2)
| Reagent | Volume | Catalogue |
|---|---|---|
| DMEM GlutaMAX, 4.5 g/L glucose (high glucose) | 500 mL | Gibco 31966-047 |
| Horse Serum | 10 mL | Gibco 16050-122 |
| Pen/Strep | 5 mL | Gibco 15140-122 |

---

\newpage

## Protocol

**Work in the biosafety cabinet. Change media every other day throughout all phases.**

### 1. Plate Coating with Matrigel *(day before or morning of seeding)*

Thaw Matrigel aliquot (BD Bioscience 354234; stored at −20°C) on ice.

Dilute 1:100 in Ham's F-10 GlutaMAX or DMEM.

| Format | Matrigel volume per well/plate |
|---|---|
| 6-well plate | 0.5 mL per well |
| 10 cm dish | 1.5 mL |
| 25 cm² flask | 1.0 mL |
| 8-well chamber slide | 0.15 mL per well |

Incubate ≥ **30 min at 37°C**. Remove by suction immediately before seeding cells.

Plate format used today: \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} \hspace{1cm} No. wells: \textcolor{red}{\_\_\_\_\_}

---

### 2. Seeding (Day 0 of GM phase)

**2.1** Thaw vial(s) rapidly at 37°C. Transfer to 15 mL Falcon tube; add growth media dropwise to 10 mL. Spin **800×g for 7 min**. Remove supernatant.

**2.2** Resuspend in growth media. Count cells if needed. Seed in Matrigel-coated plates.

| | |
|---|---|
| **Culture ID** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| **Passage** | \textcolor{red}{\_\_\_\_\_} |
| **Seeding date** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Seeding density** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} cells/well |

**2.3** Leave undisturbed in incubator. Change media every other day.

**Target:** Cells reach **80–85% confluency** before switching to DM1. This typically takes several days.

---

\newpage

### 3. Growth Media Phase — Observations

Record confluency every 1–2 days:

| Date | Day | Confluency (%) | Observations |
|---|---|---|---|
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +1 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +2 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +3 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +4 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +5 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +6 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | +7 | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |

---

### 4. Switch to DM1 *(cells 80–85% confluent)*

**4.1** Remove growth media. Replace with **DM1**. Change every other day.

**Target:** Cells reach full confluency and are visibly **aligned** (lined-up morphology) before switching to DM2. Typically ~2 days.

| | |
|---|---|
| **DM1 start date** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Confluency at switch (%)** | \textcolor{red}{\_\_\_\_\_} |

**DM1 Phase — Observations:**

| Date | Day | Confluency (%) | Alignment | Observations |
|---|---|---|---|---|
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | DM1+1 | \textcolor{red}{\_\_\_\_} | \textcolor{red}{Y / N} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | DM1+2 | \textcolor{red}{\_\_\_\_} | \textcolor{red}{Y / N} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | DM1+3 | \textcolor{red}{\_\_\_\_} | \textcolor{red}{Y / N} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |

---

\newpage

### 5. Switch to DM2 — D0

**5.1** Remove DM1. Replace with **DM2**. This is **D0**. Change media every other day.

**Target:** Harvest at **D5**. Cells should form visible myotubes by D3–D4.

| | |
|---|---|
| **DM2 start date (D0)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Confluency at switch (%)** | \textcolor{red}{\_\_\_\_\_} |
| **Target harvest date (D5)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |

**DM2 Phase — Observations:**

| Date | Day | Myotube formation | Observations |
|---|---|---|---|
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | D1 | \textcolor{red}{Y / N / partial} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | D2 | \textcolor{red}{Y / N / partial} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | D3 | \textcolor{red}{Y / N / partial} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | D4 | \textcolor{red}{Y / N / partial} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | **D5** | \textcolor{red}{Y / N / partial} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |

---

### 6. Harvest (D5)

**6.1** Record actual harvest date and confirm readiness below.

| | |
|---|---|
| **Actual harvest date** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Days in DM2** | \textcolor{red}{\_\_\_\_\_} |
| **Myotube formation observed** | \textcolor{red}{Y / N} |
| **Downstream use** | \textcolor{red}{smiFISH / RNA / other: \_\_\_\_\_\_\_\_} |

---

\newpage

## Results

Complete \texttt{results/results.csv} after harvesting.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "Differentiation Run Summary",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "4cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, media preparation issues, contamination, or unexpected morphology here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
