---
title: "Citrate Synthase Assay"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_samples  <- <<<N_SAMPLES>>>
replicates <- 3      # wells per sample; adjust if running duplicates
n_blanks   <- 3      # blank wells
excess_pct <- 10
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Samples** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagent volumes for <<<N_SAMPLES>>> samples",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Solutions

Prepare fresh on the day unless stated otherwise. Volumes below are standard batch sizes — scale up if needed.

| Solution | Target amount | Preparation | Storage |
|---|---|---|---|
| 100 mM TRIS buffer (pH 8.3) | — | 3.0275 g in 250 mL MQH\textsubscript{2}O; adjust to pH 8.3 with HCl | Fridge |
| 1 mM DTNB | 10 mL | **3.96 mg** DTNB in **10 mL** 10 mM TRIS buffer | Fridge, opaque; make every 2 weeks |
| 7.5 mM Oxaloacetate | 10 mL | **9.91 mg** in **10 mL** 100 mM TRIS buffer | **Prepare fresh daily** |
| 3 mM Acetyl CoA | 4 mL | **9.71 mg** in **4 mL** MQH\textsubscript{2}O *(or add 4.117 mL MQH\textsubscript{2}O to a 10 mg bottle)* | Fridge, opaque; make every 2 weeks |

*When the weighed amount differs from the target, adjust the buffer volume to maintain the same concentration. Record actual weights and adjusted volumes below.*

\textcolor{red}{
\begin{tabular}{|l|l|l|}
\hline
Reagent & Weight used (mg) & Adjusted buffer volume (mL) \\
\hline
DTNB & \hspace{2cm} & \hspace{2cm} \\
Oxaloacetate & & \\
\hline
\end{tabular}
}

---

## Protocol

### 1. Prepare Samples

1.1 Dilute all homogenised muscle samples to **1 mg/mL** using protein concentrations from the BCA assay.

For each sample: calculate volume of sample + volume of 100 mM TRIS buffer to reach a total of 500 µL at 1 mg/mL.

\textcolor{red}{CS assay input volumes (from BCA results):}

\vspace{3cm}

### 2. Prepare Reagent Cocktail

```{r reagent-cocktail}
n_wells <- (n_samples * replicates) + n_blanks
excess  <- 1 + excess_pct / 100

cocktail <- tibble(
  Reagent                = c("100 mM TRIS buffer", "1 mM DTNB", "3 mM Acetyl CoA"),
  `Per well (µL)`        = c(175, 10, 10),
  `Total (µL)`           = c(175, 10, 10) * n_wells,
  `Total + excess (µL)`  = round(c(175, 10, 10) * n_wells * excess, 0)
)

kable(cocktail,
      caption = sprintf("Reagent cocktail for %d samples × %d replicates + %d blanks (%d%% excess)",
                        n_samples, replicates, n_blanks, excess_pct),
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

*Note: Oxaloacetate is prepared separately and added last to initiate the reaction (see step 2.3).*

### 3. Run Assay

2.1 Pipette into each well:
  - **5 µL** sample (1 mg/mL)
  - **175 µL** TRIS buffer
  - **10 µL** DTNB
  - **10 µL** Acetyl CoA

2.2 Load blank wells with **5 µL TRIS buffer** in place of sample.

2.3 Initiate reaction by adding **10 µL Oxaloacetate** to each well. Mix immediately.

2.4 Read absorbance at **412 nm** every 30 seconds for 5 minutes.

**Plate map:**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

\vspace{3cm}

### 4. Calculate CS Activity

$$\text{CS activity} = \frac{\Delta \text{Abs}_{412} / \text{min}}{13.6 \times \text{protein concentration (mg/mL)}} \times 1000 \ [\mu\text{mol} \cdot \text{min}^{-1} \cdot \text{g protein}^{-1}]$$

---

\newpage

## Results

Complete \texttt{results/results.csv} after analysis.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "Citrate Synthase Assay Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "5cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, unusual samples, or lot number changes here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
