---
title: "RNA Quality Control — TapeStation"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_samples <- <<<N_SAMPLES>>>
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Samples** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagent volumes for <<<N_SAMPLES>>> samples",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Protocol

### 1. Preparation

1.1 Remove **High Sensitivity RNA ScreenTape** and **Sample Buffer** from fridge. Allow to equilibrate to **room temperature for 30 minutes** before use.

1.2 Thaw RNA samples on ice.

1.3 Label **`r n_samples + 1`** TapeStation tubes: one per sample plus one for the Electronic Ladder (supplied with ScreenTape).

**Samples to process:**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

**Positive control (if applicable):**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

### 2. Sample Preparation

2.1 For each sample, combine in a TapeStation tube:
  - **2 µL** High Sensitivity RNA Sample Buffer
  - **1 µL** RNA sample

*Note: be careful when dispensing the Sample Buffer from a new tube — extra droplets on the pipette tip can dilute the sample. Expel once into waste before loading.*

2.2 Vortex tubes using the IKA vortex adapter for **1 minute at 2000 rpm**.

2.3 Spin briefly to collect contents.

2.4 Denature at **72°C for 3 minutes**, then place **immediately on ice for 2 minutes**.

### 3. Run TapeStation

3.1 Load tubes and ScreenTape into the TapeStation instrument.

3.2 Run analysis. Export results as PDF and CSV.

**Well layout:**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

\vspace{3cm}

---

\newpage

## Results

Complete \texttt{results/results.csv} from the TapeStation output. Fill in well, RIN, 28S/18S ratio, and concentration per sample.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "TapeStation RNA QC Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 7) %>%
  column_spec(1, width = "4cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations, degraded samples, or lot number changes here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
