---
title: "Mitochondrial RNA Extraction"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Samples** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagent volumes for <<<N_SAMPLES>>> samples",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

Note: prepare +1 extra set of volumes for the DNase mastermix tube.

---

\newpage

## Protocol

### 1. Preparation

**For each sample, label:**

- 1$\times$ Zymo-Spin IC Column
- 3$\times$ Collection Tube
- 2$\times$ RNase-Free Tube

1.1 Clean all surfaces with RNaseZap and 70% ethanol. Use filter tips and RNA-dedicated bagged tubes throughout.

**Samples to process:**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

**Storage location (e.g. Fatboy box and shelf):**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

### 2. Homogenise Samples

2.1 In a **fume hood**, thoroughly homogenise mitochondrial pellets stored in TRIzol. Use pestle and/or vortex until the pellet is fully dissolved.

2.2 Incubate at **room temperature for 5 minutes**.

2.3 To remove insoluble debris, centrifuge at **13,000×g for 2 minutes**. Transfer supernatant to a new RNase-free tube; discard pellet.

\newpage

### 3. RNA Purification

**NOTE:** All steps at room temperature. Centrifuge at **15,000×g for 30 seconds** unless stated otherwise. Bring vortex into fume hood for step 3.1.

3.1 **While in the fume hood**: add **400 µL ethanol (95–100%)** to the TRIzol-lysed supernatant. Mix thoroughly by vortex.

3.2 Incubate at **room temperature for 10 minutes**.

3.3 Transfer the mixture into a Zymo-Spin IC Column seated in a collection tube. Centrifuge (**outside fume hood**). Move column to a new collection tube; discard flow-through.

**Remaining steps can be completed outside the fume hood.**

3.4 **DNase Treatment**

3.4.1 Add **400 µL RNA Wash Buffer** to column. Centrifuge. Discard flow-through.

3.4.2 In an RNase-free tube, combine **5 µL DNase I** (6 U/µL) + **35 µL DNA Digestion Buffer** per sample. Mix by **gentle inversion**. Add mastermix directly to column matrix.

3.4.3 Incubate at **room temperature for 15 minutes**.

3.5 Add **400 µL Direct-zol RNA Pre-Wash** to column. Centrifuge. Discard flow-through. **Repeat this step once more.**

3.6 Add **700 µL RNA Wash Buffer** to column. Centrifuge for **1 minute** to ensure complete removal. Repeat once more: centrifuge for **30 seconds without adding buffer** to fully dry the column matrix. Transfer column carefully to a new RNase-free tube.

3.7 Elute: add **\textcolor{red}{15 µL}** DNase/RNase-Free Water directly to the column matrix. Incubate at **room temperature for 2 minutes**. Centrifuge.

**Store extracted RNA at:** \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

---

\newpage

## Results

Complete \texttt{results/results.csv} after the extraction. Record any per-sample deviations in the notes column.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "RNA Extraction Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "4cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, unexpected observations, or lot number changes here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
