---
title: "Satellite Cell Isolation from Human Skeletal Muscle Biopsy"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_biopsies <- <<<N_SAMPLES>>>
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Biopsies** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagents and materials",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Protocol

**Work in the biosafety cabinet throughout. All solutions pre-warmed to 37°C unless stated.**

### 1. Preparation

#### 1.1 Turn on heat oven at 37°C

#### 1.2 Prepare solutions

**Ham's F-10 + P/S (transport buffer)**

- 500 mL Ham's F-10 GlutaMAX (Gibco 41550)
- 5 mL Pen/Strep (Gibco 15140)

**Growth media**

- 500 mL Ham's F-10 GlutaMAX (Gibco 41550)
- 100 mL FBS (Gibco 10270)
- 5 mL Pen/Strep (Gibco 15140)
- 5 mL Fungizone Amphotericin B 250 µg/mL (Gibco 15290)

**Digestion buffer** *(make fresh; sterile filter before use)*

Per `r n_biopsies` biopsy/biopsies:

| Reagent | Amount |
|---|---|
| Trypsin 1× | `r 5 * n_biopsies` mL |
| Collagenase IV (C5138, Sigma) | `r 10 * n_biopsies` mg |
| Ham's F-10 GlutaMAX | `r 5 * n_biopsies` mL |
| BSA (A8806, Sigma) | `r 50 * n_biopsies` mg |

Sterile-filter through a 0.2 µm Minisart filter into **2 × 15 mL Falcon tubes** (`r 5 * n_biopsies` mL each). Warm to 37°C.

#### 1.3 Coat flask with Matrigel *(do during pre-plating step 6)*

Thaw Matrigel aliquot (BD Bioscience 354234; 0.5 mL at −20°C) on ice.

- Dilute 1:100 in Ham's F-10 GlutaMAX or DMEM.
- Add **1 mL** to a 25 cm² flask.
- Incubate ≥ 30 min at 37°C.
- Remove matrigel by suction just before transferring cells.

---

\newpage

### 2. Biopsy Processing

**2.1** Collect biopsy in a 15 mL Falcon tube with ~5 mL ice-cold Ham's F-10 + P/S.
Keep on ice. **Isolation must occur the same day as biopsy.**

Record biopsy details:

| | Biopsy 1 |
|---|---|
| **Participant / Donor ID** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Culture ID (P0)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Biopsy mass (mg)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Biopsy time** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |

**2.2** Pour biopsy into a 60 mm Petri dish. Pick muscle pieces into the **lid** containing ~5 mL warm digestion buffer. Remove fat (floating pieces) and connective tissue. Mince muscle into small pieces with sterile scissors.

**2.3** Save the transport media from the Falcon tube **(media 1)** — centrifuge separately to recover satellite cells already liberated.

**2.4** Transfer minced muscle + 5 mL digestion buffer into a 15 mL Falcon tube. Incubate at **37°C for 5 min**, gently inverting the tube.

**2.5** While incubating: centrifuge **media 1** at **800×g for 5 min**. Discard supernatant. Dissolve pellet in **5 mL fresh digestion buffer** — this will be added to the second digestion round.

**2.6** Let muscle pieces (from step 2.4) settle to the bottom. Transfer supernatant into a tube containing **2 mL FBS on ice** to inactivate trypsin/collagenase. Add the media 1 pellet suspension (step 2.5) to the remaining muscle pieces. Incubate at **37°C for 10–15 min**.

**Second digestion duration:** \textcolor{red}{\_\_\_\_\_ min}

**2.7** Filter both digested suspensions (ice-cold FBS fraction + muscle piece fraction) through a **70 µm cell strainer** into a 50 mL Falcon tube.

**2.8** Spin at **800×g for 7 min**. Remove supernatant with suction.

**2.9** Wash cells in **10 mL Ham's F-10 + P/S**. Spin at **800×g for 7 min**. Remove supernatant with suction.

---

### 3. Pre-Plating *(fibroblast depletion)*

**3.1** Resuspend pellet in **3 mL growth media**. Transfer to a **60 mm Petri dish** (uncoated).

**3.2** Incubate at 37°C for **3 hours** to allow fibroblasts and other adherent cells to attach.

Pre-plating start time: \textcolor{red}{\_\_\_\_\_\_\_\_\_} \hspace{1cm} Expected transfer time: \textcolor{red}{\_\_\_\_\_\_\_\_\_}

*During this incubation: prepare Matrigel-coated 25 cm² flask (step 1.3 above).*

---

### 4. Transfer to Flask

**4.1** Without disturbing the attached cells (fibroblasts), collect the cell suspension from the 60 mm dish.

**4.2** Remove Matrigel from the 25 cm² flask by suction. Transfer cell suspension to the flask.

**4.3** Rinse the 60 mm dish with an additional **2 mL growth media** (pipette gently against the edge; do not dislodge attached cells). Add to the flask.

**4.4** Label flask: **Culture ID, date, initials, P0**.

**4.5** Place flask in incubator. **Do not disturb for 4 days.**

Transfer time: \textcolor{red}{\_\_\_\_\_\_\_\_\_} \hspace{1cm} Operator: \textcolor{red}{\_\_\_\_\_\_\_\_\_}

---

\newpage

### 5. Ongoing Culture *(post-isolation)*

Change media every 2 days. Colonies typically form within **7–10 days**.

| Day | Date | Action | Observations |
|---|---|---|---|
| +4 | \textcolor{red}{\_\_\_\_\_\_\_} | First media change | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| +6 | \textcolor{red}{\_\_\_\_\_\_\_} | Media change | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| +8 | \textcolor{red}{\_\_\_\_\_\_\_} | Media change | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| +10 | \textcolor{red}{\_\_\_\_\_\_\_} | Media change / check confluency | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |

---

### 6. P0 Trypsination *(when colonies have formed)*

**6.1** Remove media. Add **1 mL TrypLE** and remove with suction immediately.

**6.2** Add **0.5 mL TrypLE**. Incubate **2 min** in incubator. Check cells are released.

**6.3** Add **7 mL growth media**. Label flask **P0 + date**.

---

### 7. Passage to P1 and Freeze *(when cells ~70% confluent in P0 flask)*

**7.1** Remove media. Add **1 mL TrypLE** and remove with suction.

**7.2** Add **1 mL TrypLE**. Incubate **2 min**. Check cells are released.

**7.3** Add **10 mL growth media**. Transfer to **100 mm Petri dish** coated with **1.5 mL Matrigel** (1:100 dilution, 30 min 37°C). Label **P1 + date**.

**7.4** When cells reach **75–80% confluency**: freeze as follows.

  - Remove media. Add **1 mL TrypLE**, remove with suction.
  - Add **1.5 mL TrypLE**, 2 min — check cells released.
  - Add **10 mL growth media**, pipette up and down. Transfer to 15 mL Falcon tube.
  - Spin **800×g for 7 min**.
  - Prepare DMSO/FBS (1:10 — 1 mL DMSO + 9 mL FBS).
  - Label **3 cryo tubes**: top — P1 + number; side — HSkM, number, P1, date, study, initials.
  - Resuspend pellet in **3 mL DMSO/FBS**. Aliquot 1 mL per cryo tube.
  - Transfer to isopropanol freezing box → **−80°C**.

| | Culture |
|---|---|
| **Culture ID (P1)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Date frozen** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **No. vials** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Storage box** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |

---

\newpage

## Results

Complete \texttt{results/results.csv} after isolation is complete.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "Satellite Cell Isolation Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "4cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, yield observations, or contamination issues here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
