---
title: "smiFISH Probe Assay"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_wells <- <<<N_SAMPLES>>>
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Wells** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagents and materials",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Experiment Setup

| | |
|---|---|
| **Differentiation run ID** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Culture ID** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Days in DM2 at fixation** | \textcolor{red}{\_\_\_\_\_} |
| **Plate format** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Microscope / system** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Objective** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |
| **Image analysis software** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_} |

### Probes used

\textcolor{red}{List probes, target genes, and channels below.}

| Well | Probe name | Target gene | Channel | Notes |
|---|---|---|---|---|
| \textcolor{red}{\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| \textcolor{red}{\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_} |

---

\newpage

## Protocol

### 1. Fixation

**1.1** Remove media. Rinse wells gently with **1× PBS**.

**1.2** Fix cells with **4% paraformaldehyde** in PBS.

| Format | Volume | Duration |
|---|---|---|
| 6-well | 1 mL/well | 10 min, RT |
| 8-well chamber slide | 200 µL/well | 10 min, RT |

**1.3** Remove PFA (\textcolor{red}{dispose in PFA waste}). Wash **3× PBS** (5 min each).

Fixation time: \textcolor{red}{\_\_\_\_\_\_\_\_\_} \hspace{1cm} Operator: \textcolor{red}{\_\_\_\_\_\_\_\_\_}

---

### 2. Permeabilisation

**2.1** Add **70% ethanol** to wells.

| Format | Volume |
|---|---|
| 6-well | 1 mL/well |
| 8-well chamber slide | 200 µL/well |

**2.2** Incubate **overnight at 4°C** (or minimum 1 hour). Cells can be stored in 70% EtOH at 4°C for up to 1 week at this stage.

---

### 3. Pre-Hybridisation Wash

**3.1** Prepare **Wash Buffer**: 10% formamide + 2× SSC in RNase-free water.

**3.2** Remove ethanol. Wash wells **2×** with Wash Buffer (5 min each, RT).

---

\newpage

### 4. Hybridisation

**4.1** Prepare **Hybridisation Buffer** (per well):

| Reagent | Amount |
|---|---|
| Formamide (deionised) | 10% v/v |
| Dextran sulfate | 10% w/v |
| 20× SSC | to 2× final |
| RNase-free BSA | 1 mg/mL |
| RNase-free water | to volume |

\textcolor{red}{Add probe(s) at validated concentration. Record concentrations below.}

| Probe | Stock concentration | Working concentration | Volume added |
|---|---|---|---|
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} |
| \textcolor{red}{\_\_\_\_\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} | \textcolor{red}{\_\_\_\_\_} |

**4.2** Remove wash buffer. Add hybridisation buffer + probe(s) to wells. Cover with parafilm to prevent evaporation.

**4.3** Incubate **overnight at 37°C** in humidified chamber (or incubator).

Hybridisation start time: \textcolor{red}{\_\_\_\_\_\_\_\_\_}

---

### 5. Post-Hybridisation Washes

**5.1** Remove hybridisation buffer. Wash **2× Wash Buffer** (30 min each, 37°C).

**5.2** (Optional) Add **DAPI** (1 µg/mL in PBS) during first wash. Incubate 10 min.

**5.3** Final wash: **1× PBS** (5 min, RT).

---

### 6. Mounting and Imaging

**6.1** Mount with anti-fade mounting medium. Apply coverslip. Seal edges with nail varnish.

**6.2** Image on confocal or widefield fluorescence microscope. Record settings:

| Parameter | Value |
|---|---|
| **Microscope** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| **Objective** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |
| **Exposure (channel 1)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_} ms |
| **Exposure (channel 2)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_} ms |
| **Z-stack (step size / n slices)** | \textcolor{red}{\_\_\_\_\_\_\_\_\_} |
| **Fields of view per well** | \textcolor{red}{\_\_\_\_\_} |
| **Image storage path** | \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_} |

---

\newpage

## Results

Complete \texttt{results/results.csv} after image analysis is complete.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "smiFISH Assay Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "1.5cm") %>%
  column_spec(2, width = "3cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, probe performance observations, imaging issues, or analysis decisions here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
