---
title: "Whole Muscle Homogenisation"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

# Buffer component ratios (supervisor's proportions — per 12 mL total solution)
# Homogenisation buffer: Western Lysis Buffer
#   50 mM TRIS, 1 mM EDTA, 10% Glycerol, 1% Triton X-100, pH 7.5
ratio_buffer    <- 10.8 / 12   # 90.0%
ratio_water     <- 1.14 / 12   # 9.5%
ratio_inhibitor <- 0.06 / 12   # 0.5% — PIC usable for ~30 min once added

ul_per_mg <- 20  # µL homogenisation solution required per mg tissue
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Samples** | <<<N_SAMPLES>>> |

---

## Input

Place `input/muscle_partitioning.csv` in this directory before running. Required columns: `mouse_id`, `weight_mg`.

```{r load-input}
partitioning <- read_csv("input/muscle_partitioning.csv", show_col_types = FALSE)

# Optional: un-comment to exclude specific mice
# partitioning <- partitioning %>% filter(!mouse_id %in% c("BB000"))

partitioning <- partitioning %>%
  mutate(
    solution_ul = weight_mg * ul_per_mg,
    sample_id   = paste0("<<<DATE>>>_", mouse_id, "_homogenised-muscle")
  ) %>%
  arrange(mouse_id)
```

---

## Buffer Preparation

\textcolor{red}{PIC is only usable for \textbf{~30 minutes} once added. For large batches, prepare the buffer without PIC and split into sub-batches — add PIC to each sub-batch immediately before use.}

```{r buffer-volumes}
total_ul           <- sum(partitioning$solution_ul, na.rm = TRUE)
total_ml           <- total_ul / 1000
total_with_excess  <- ceiling(total_ml * 1.10)  # 10% excess

buffer_tbl <- tibble(
  Component = c(
    "Homogenisation buffer (Western Lysis Buffer)",
    "ddH\\textsubscript{2}O (milliQ)",
    "Protease inhibitor cocktail (PIC)"
  ),
  `Volume (mL)` = round(
    c(
      total_with_excess * ratio_buffer,
      total_with_excess * ratio_water,
      total_with_excess * ratio_inhibitor
    ), 2
  )
)

kable(buffer_tbl,
      caption   = sprintf("Homogenisation buffer for %d samples (%.1f mL required + 10%% excess = %.1f mL total)",
                          nrow(partitioning), total_ml, total_with_excess),
      booktabs  = TRUE,
      escape    = FALSE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

**Buffer composition (Western Lysis Buffer):**
50 mM TRIS · 1 mM EDTA · 10% Glycerol · 1% Triton X-100 · pH 7.5

\textcolor{red}{Verify buffer lot number: \_\_\_\_\_\_\_\_\_\_\_ \quad PIC lot number: \_\_\_\_\_\_\_\_\_\_\_}

---

## Sample Volumes

```{r sample-volumes}
kable(
  partitioning %>% select(mouse_id, weight_mg, solution_ul, sample_id),
  col.names = c("Mouse ID", "Tissue weight (mg)", "Buffer required (µL)", "Sample ID"),
  caption   = sprintf("Homogenisation volume per sample (%d µL per mg tissue)", ul_per_mg),
  booktabs  = TRUE
) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9)
```

---

\newpage

## Protocol

### 1. Preparation

1.1 Prepare homogenisation buffer (without PIC) and keep on ice.

1.2 Label one pestle per sample. If samples exceed one batch (~30 min of work), split into sub-batches and prepare PIC separately for each.

1.3 Remove samples from --80°C and thaw on ice.

### 2. Homogenisation

2.1 Add PIC to the first batch of buffer immediately before starting.

2.2 Add the calculated volume of homogenisation buffer to each sample tube (see Table 2).

2.3 Homogenise each sample with **20 up-and-down strokes** of the pestle.

2.4 Repeat step 2.3 **5 times** (100 strokes total) until the homogenate takes on a **cloudy appearance**.

2.5 If batching: once first batch is complete, add PIC to the next batch of buffer and continue.

### 3. After Homogenisation

3.1 Samples can be **frozen at --80°C** for later BCA assay, or processed immediately.

3.2 Record any deviations — unusual tissue appearance, insufficient homogenisation, missed samples.

---

## Results

Complete `results/results.csv` after the experiment. Sample IDs are pre-populated from Table 2 above.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption  = "Homogenisation results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "5cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, batching decisions, or lot number changes here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
