---
title: "Isolation of Mitochondria from Human Skeletal Muscle Tissue"
subtitle: "<<<PROJECT_NAME>>>"
date: "<<<DATE>>>"
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)

n_samples <- <<<N_SAMPLES>>>
total_volume <- function(vol_per_sample) vol_per_sample * n_samples
```

| | |
|---|---|
| **Experiment ID** | <<<EXPERIMENT_ID>>> |
| **Date** | <<<DATE>>> |
| **Samples** | <<<N_SAMPLES>>> |

---

## Consumables

```{r consumables}
<<<CONSUMABLES_R>>>

kable(consumables_df,
      caption = "Reagent volumes for <<<N_SAMPLES>>> samples",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, bold = TRUE)
```

\textcolor{red}{Verify lot numbers against physical tubes before starting. Update input/consumables.csv with any changes.}

---

\newpage

## Protocol

**Keep all samples and solutions on ice throughout. Centrifuge at 4°C unless stated.**

In this protocol, **<<<N_SAMPLES>>>** samples + an additional 3 spares will be processed.

**Samples to process:**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

### 1. Preparation

#### Day Before

##### 1.1 Label Tubes, Beakers and Other Materials

**1× each of the following (shared across all samples):**

- 1× 50 mL tube — liquid waste
- 1× 50 mL tube — Protease Inhibition Buffer
- 1× 50 mL tube — 1× Solution 2
- 1× 15 mL Falcon tube — Extraction Buffer
- 1× large beaker — 1× Separation Buffer *(see step 1.2.5 for volume)*
- 1× large beaker — ddH\textsubscript{2}O
- 1× 50 mL tube — Solution 3
- 2× 2 mL Eppendorf tubes — RNase-A and Proteinase-K solutions

**Per sample:**

- 1× 2 mL Eppendorf tube — sample collection
- 1× 1.7 mL Eppendorf tube — flushing and storage of mitochondria
- 1× gentleMACS tube (purple lid) — tissue dissociation
- 2× 15 mL Falcon tubes
- 1× Pre-Separation Filter 70 µm
- 1× Pre-Separation Filter 30 µm

##### 1.2 Reagent Preparation (Day Before)

Prepare **`r total_volume(2100) / 1000` mL** of **Solution 3** in a 50 mL tube and store at −20°C.
*Note: 2.1 mL required per 50–100 mg tissue.*

---

#### Morning of (~1 hour before dissection)

*Note: Two buckets of ice required — one to cool reagents, one to bring to the processing room.*

**1.2.1** Thaw **`r total_volume(2100) / 1000` mL** of **Solution 3** and keep on ice.

**1.2.2** Prepare **`r total_volume(2500) / 1000` mL** of **1× Solution 2**: add **`r total_volume(250) / 1000` mL** of 10× Solution 2 to **`r total_volume(2250) / 1000` mL** ddH\textsubscript{2}O. Keep on ice.
*Note: up to 2.5 mL required per sample (2 mL for Protease Inhibition Buffer, 0.5 mL for Extraction Buffer).*

**1.2.3** Prepare **`r total_volume(2000) / 1000` mL** of **Protease Inhibition Buffer**: add **`r total_volume(10)` µL** Protease Inhibitor Cocktail to **`r total_volume(2000) / 1000` mL** freshly prepared 1× Solution 2.
*Note: once made, usable for ~30 minutes only. For large batches, prepare in multiple rounds.*

**1.2.4** Prepare **`r total_volume(500) / 1000` mL** of **Extraction Buffer**: add **`r total_volume(18)` µL** of Solution 1 to **`r total_volume(500) / 1000` mL** 1× Solution 2. Keep on ice.
*Note: 0.5 mL required per 50–100 mg tissue.*

**1.2.5** Prepare **`r total_volume(23000) / 1000` mL** of **1× Separation Buffer**: warm 10× Separation Buffer at 37°C until crystals are dissolved. Add **`r total_volume(2300) / 1000` mL** 10× Separation Buffer to **`r total_volume(20700) / 1000` mL** ddH\textsubscript{2}O. Pre-cool on ice.

**1.2.6** Add **0.5 mL** ice-cold Extraction Buffer to each of **`r n_samples`** × 2 mL Eppendorf tubes. Keep on ice.

**1.2.7** Place **`r n_samples`** × gentleMACS tube(s) on ice to pre-cool.

#### RNase-A and Proteinase-K Preparation

*These solutions are sufficient for ALL samples — do not prepare one per sample. Can be prepared during the 1-hour incubation at step 3.3.*

**1.2.8** Prepare **RNase-A solution (1.1 mg/mL)**: add 11 µL RNase-A (100 mg/mL) to 989 µL ice-cold Storage Buffer. Keep on ice.

**1.2.9** Prepare **Proteinase-K solution (0.24 µg/µL)**: add 12 µL of 20 µg/µL stock to 988 µL Storage Buffer. Keep on ice.

---

\newpage

### 2. Homogenisation

Take ice bucket with **`r n_samples`** × 2 mL Eppendorf tube(s) (each containing 0.5 mL Extraction Buffer) to the processing lab biopsy room.

#### 2.1 Dissect and Collect Samples

**2.1.1** Obtain fresh skeletal muscle tissue (~100 mg per sample). Record weights:

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

**Tissue weights (mg):**

\textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

**2.1.2** Add tissue to each 2 mL tube containing 0.5 mL ice-cold Extraction Buffer. Mince with dissection scissors into ~1–2 mm pieces. Incubate on ice for **30 minutes**.

#### 2.2 Tissue Homogenisation

Bring ice bucket back to PC2 lab to complete homogenisation.

**2.2.1** Centrifuge **`r n_samples`** × 2 mL tubes at **300×g for 5 min** at 4°C. Discard supernatant.

**2.2.2** Add **1 mL** Protease Inhibition Buffer to each tube. Gently flick to resuspend pellet.

**2.2.3** Pour suspension into pre-cooled gentleMACS tube(s).

**2.2.4** Rinse each Eppendorf tube with an additional **1 mL** ice-cold Protease Inhibition Buffer and add to the same gentleMACS tube(s).

**2.2.5** Tightly close gentleMACS tube(s) and attach upside-down onto the gentleMACS Dissociator sleeve.

**2.2.6** Run program: `h_mito_tissue_01`.

**2.2.7** Detach tube(s) and centrifuge at **200×g for 90 seconds** at 4°C to collect homogenate at tube bottom.

**2.2.8** Place **`r n_samples`** × 15 mL Falcon tube(s) on ice. Place a Pre-Separation Filter (70 µm) on top of each. Transfer homogenate into filter reservoir and allow to run through.

**2.2.9** Wash each filter with **2 × 1 mL** ice-cold Solution 3. Centrifuge filtered homogenate at **500×g for 5 min** at 4°C. Transfer supernatant (containing mitochondria) to new **`r n_samples`** × 15 mL Falcon tube(s).

---

\newpage

### 3. Mitochondrial Isolation

**3.1** Add 1× Separation Buffer to each Falcon tube (from step 2.2.9) to bring total volume to **10 mL**.

**3.2** Add **50 µL** human Anti-TOM22 MicroBeads to each Falcon tube to magnetically label mitochondria.

**3.3** Mix well. Incubate for **1 hour** in fridge at 2–8°C under continuous rotation (~12 rpm) using MACSmix Tube Rotator.
*Note: prepare columns (steps 3.4–3.5) and RNase-A/Proteinase-K solutions (steps 1.2.8–1.2.9) during this incubation if not done earlier.*

**3.4** Place **`r n_samples`** × LS Column(s) in the magnetic field of a MACS separator. Place a Pre-Separation Filter (30 µm) on top of each LS column.

**3.5** Equilibrate each LS column by rinsing with **3 mL** 1× Separation Buffer.

**3.6** Apply magnetically labelled mitochondria to the LS column. Allow to run through.
*Note: apply in 3 × 3.3 mL aliquots; add each only when the reservoir is empty.*

**3.7** Wash LS column with **3 × 3 mL** 1× Separation Buffer.
*Note: add each wash only when the column reservoir is empty.*

**3.8** Remove LS column from separator and place on a 1.7 mL Eppendorf tube.

**3.9** Pipette **1.4 mL** 1× Separation Buffer onto the LS column. Immediately flush out enriched mitochondria by firmly pushing the plunger into the column.

---

### 4. RNase and Proteinase-K Treatment

**4.1** Centrifuge at **13,000×g for 2 min**. Discard supernatant.

**4.2** Wash pellet **twice** with 1 mL Storage Buffer, centrifuging each time.

**4.3** Resuspend pellet in **100 µL** Storage Buffer.

**4.4** Gently disrupt pellet with a wide-bore pipette tip and plastic pestle (avoid twisting) until homogeneous.

**RNase-A Treatment** [final concentration: 100 µg/mL]

Add **10 µL** of the 1.1 mg/mL RNase-A solution to the 100 µL mitochondrial suspension. Incubate on ice for **30 min**, flicking every 10 min.

**Proteinase-K Treatment** [final concentration: 20 µg/mL]

After 30 min RNase-A treatment, add **10 µL** of 0.24 µg/µL Proteinase-K. Incubate on ice for **30 min**, flicking every 10 min.

**Final Wash**

Centrifuge at **13,000×g for 2 min**. Discard supernatant. Wash pellet **twice** in 1 mL Storage Buffer.

---

### 5. Storage in TRIzol

**5.1** Add **400 µL** TRI Reagent Solution to each tube.

**5.2** Disrupt pellet with repeated pipetting.

**5.3** Store at **−80°C** for RNA extraction.

**Store in:** \textcolor{red}{\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

---

\newpage

## Results

Complete \texttt{results/results.csv} after the isolation.

```{r results-table}
<<<RESULTS_R>>>

kable(results_df,
      caption = "Mitochondrial Isolation Results",
      booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "5cm")
```

---

## Deviations / Notes

\textcolor{red}{Record any deviations from protocol, yield issues, sample-specific observations, or lot number changes here.}

\vspace{3cm}

---

*Generated by generate\_experiment.py — experiment\_id <<<EXPERIMENT_ID>>>*
